```{r}
source("Rscripts/Fire-peak-df.R")
```

# read in data
```{r}
k562_fire_all=my_read_bed("../FIREv2.0/Revision-1/just-more-samples/results/K562-PS00075/FDR-peaks/FDR.track.bed.gz")
k562_dnase_peaks = my_read_bed("data/k562-data/K562.peaks.bed.gz")
k562_dnase_signal = my_read_bed("data/k562-data/K562.signal.bg.gz")
```

# overlap with all fire data
```{r}
k562_fire_all = k562_fire_all %>%
    bed_map(
        k562_dnase_peaks,
        is_dnase_peak = n() > 0
    ) %>%
    bed_map(
        k562_dnase_signal,
        dnase_max = max(V4)
    ) %>%
    replace_na(
        list(
            is_dnase_peak = FALSE,
            dnase_max = 0
        )
    ) 
```

# overlap with peaks
```{r}
k562 = my_read_bed(
    "../FIREv2.0/Revision-1/just-more-samples/results/K562-PS00075/FDR-peaks/FDR-FIRE-peaks.bed.gz"
    ) %>%
    bed_map(
        k562_dnase_peaks,
        is_dnase_peak = n() > 0
    ) %>%
    bed_map(
        k562_dnase_signal,
        dnase_max = max(V4)
    ) %>%
    replace_na(
        list(
            is_dnase_peak = FALSE,
            dnase_max = 0
        )
    ) 
k562 = k562 %>% mutate(
    psize=end-start,
    size_group = cut(psize, breaks=c(0,200,250,Inf)),
    ) %>%
    group_by(size_group, is_dnase_peak) %>%
    mutate(
        size_group_label = paste(size_group, " n=", comma(n()), sep="")
    )
```

```{r}
k562_dnase_or_fire = bind_rows(
    list(
        k562_dnase_peaks %>% select(chrom,start,end),
        k562 %>% select(chrom,start,end)
    )
) %>% valr::bed_merge() %>%
bed_map(
    k562_dnase_signal,
    dnase_max = max(V4)
) %>%
bed_map(
    k562_dnase_peaks,
    is_dnase_peak = n() > 0
) %>%
bed_map(
    k562_fire_all,
    fire_max=max(fire_coverage/coverage*100),
) %>%
bed_map(
    k562,
    is_fire_peak = n() > 0,
) %>%
replace_na(
    list(
        dnase_max = 0,
        fire_max = 0,
        is_dnase_peak = FALSE,
        is_fire_peak = FALSE
    )
)
k562_dnase_or_fire
```

# dnase
```{r}
k562 %>%
    filter(dnase_max > 0) %>%
    filter(is_dnase_peak) %>%
    ggplot(aes(y=score, x=dnase_max)) +
    geom_hex(bins=30) +
    scale_fill_distiller("", palette = "Spectral", trans="log10") +
    stat_cor()+
    #geom_smooth(method="lm", se=F) +
    #facet_wrap(~autosome, ncol=2)+
    #facet_wrap(~group)+
    scale_x_continuous(
        "DNase peak signal",
        labels=comma,
        trans="log10",
    ) +
    annotation_logticks(side="b") +
    scale_y_continuous(
        "FIRE peak score",
        labels=comma,
        #trans="log10",
    ) + 
    my_grid() +
    theme(
        aspect.ratio=1,
    )
my_ggsave("Figures/k562-DNase-vs-FIRE.pdf", height=3, width=4)
```

# union fire and dnase peaks 
```{r}
k562_dnase_or_fire %>%
    ggplot(aes(y=fire_max, x=dnase_max+0.001)) +
    geom_hex(bins=30) +
    scale_fill_distiller("", palette = "Spectral", trans="log10") +
    stat_cor()+
    #geom_smooth(method="lm", se=F) +
    #facet_wrap(~autosome, ncol=2)+
    #facet_wrap(~group)+
    scale_x_continuous(
        "DNase peak signal",
        labels=comma,
        trans="log10",
    ) +
    annotation_logticks(side="b") +
    scale_y_continuous(
        "FIRE peak score",
        labels=comma,
        #trans="log10",
    ) + 
    #facet_row(~paste0(is_dnase_peak, is_fire_peak)) +
    my_grid() +
    theme(
        aspect.ratio=1,
    )
my_ggsave("Figures/k562-all-DNase-vs-FIRE.pdf", height=2, width=3)
    ```


# dnase by peak size
```{r}
z = k562 %>%
 filter(dnase_max > 0) %>%
    filter(is_dnase_peak) %>%
    ggplot(aes(y=score, x=dnase_max)) +
    geom_hex(bins=30) +
    scale_fill_distiller("", palette = "Spectral", trans="log10") +
    stat_cor()+
    #geom_smooth(method="lm", se=F) +
    #facet_wrap(~autosome, ncol=2)+
    #facet_wrap(~group)+
    scale_x_continuous(
        "DNase peak signal",
        labels=comma,
        trans="log10",
    ) +
    annotation_logticks(side="b") +
    facet_row(~size_group_label) +
    scale_y_continuous(
        "FIRE peak score",
        labels=comma,
        #trans="log10",
    ) + 
    my_grid() +
    theme(
        aspect.ratio=1,
    )
        
my_ggsave("Figures/k562-FIRE-vs-DNase-by-size.pdf", height=2, width=6)

```


# regression by size
```{r}
box_regions = k562 %>%
 filter(dnase_max > 0) %>%
    filter(is_dnase_peak) %>%
    mutate(
        dnase_cut = cut(
            dnase_max, 
            breaks=c(0, 0.1, 0.25, 0.5, 0.75, 1, 2.5, 5, 7.5, 10, 25, 50),
        ),
        fire_cut = cut(100*fire_coverage/coverage, breaks=seq(0, 100, 10)),
        fire_frac=fire_coverage/coverage,
    ) %>%
    group_by(dnase_cut, size_group)

fake_zero_zero = box_regions %>%
    group_by(size_group_label) %>%
    sample_n(1) %>%
    mutate(
        dnase_max = 0,
        fire_coverage = 0,
    )

box_regions = bind_rows(
    list(
        #fake_zero_zero, 
        box_regions
    )
)

fit <- lm(dnase_max ~ fire_frac * size_group_label, data = box_regions)
summary(fit)
# predictions for 50% fire coverage
pred = data.frame(
    fire_frac = sort(rep(c(0.25, 0.5, 0.75), 3)),
    size_group_label = rep(unique(box_regions$size_group_label),3)
)
pred$dnase_max=predict(fit, newdata=pred)
pred

formula <- y ~ x 
z = box_regions %>% 
    ggplot(aes(x=fire_frac, y=dnase_max, color=size_group_label)) +
    geom_smooth(method="lm", 
        se=F,
        formula=formula,
    ) +
    #stat_cor(label.y=c(8,9,10),label.x=0.5,)+ 
    stat_regline_equation(
        aes(label =  paste(..eq.label..)),
        label.y=8.5+1.1*c(0,.5,1),
        size=3,
        formula=formula,
    ) +
    geom_text_repel(
        data=pred %>% filter(fire_frac==0.5),
        aes(label=round(dnase_max,2)),
        color="black",
        size=2,
        nudge_y=0.75,
        #direction="y",
        arrow=arrow(type="closed", length=unit(0.005, "npc")),
        min.segment.length=0,
    ) +
    my_grid() + 
    scale_y_continuous(
        "K562 DNase peak signal",
        labels=comma,
    #    trans="log10",
    )+
    scale_x_continuous(
        "K562 FIRE % actuation",
        labels=percent,
        #limits=c(0,1),
    ) + 
    scale_color_manual(
        "",
        values = c("darkorange", "darkred", "darkblue"),
    ) +
    #coord_flip() +
    theme(
        legend.position="top",
        aspect.ratio=1,
    )

my_ggsave("Figures/k562-FIRE-vs-DNase-by-size-regression.pdf", height=3, width=3)
```

```{r}
d = k562 %>% filter(is_dnase_peak) %>% mutate(fire_acc = fire_coverage/coverage)

fit <- lm(dnase_max ~ psize * fire_acc, data = d)
summary(fit)
af <- anova(fit)
afss <- af$"Sum Sq"
cbind(af,PctExp=afss/sum(afss)*100)

fit <- lm(dnase_max ~ psize, data = d)
summary(fit)
af <- anova(fit)
afss <- af$"Sum Sq"
cbind(af,PctExp=afss/sum(afss)*100)

```
Call:
lm(formula = dnase_max ~ psize * fire_acc, data = d)

Residuals:
    Min      1Q  Median      3Q     Max 
-20.165  -0.712  -0.150   0.390  74.304 

Coefficients:
                 Estimate Std. Error t value Pr(>|t|)    
(Intercept)    -0.2281745  0.0417618  -5.464 4.67e-08 ***
psize          -0.0020502  0.0002084  -9.839  < 2e-16 ***
fire_acc       -0.3759709  0.0723159  -5.199 2.01e-07 ***
psize:fire_acc  0.0305333  0.0003130  97.566  < 2e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 1.689 on 99108 degrees of freedom
Multiple R-squared:  0.608,     Adjusted R-squared:  0.608 
F-statistic: 5.124e+04 on 3 and 99108 DF,  p-value: < 2.2e-16

                  Df    Sum Sq      Mean Sq   F value Pr(>F)    PctExp
psize              1 257148.04 2.571480e+05 90171.931      0 35.665861
fire_acc           1 154066.57 1.540666e+05 54025.225      0 21.368691
psize:fire_acc     1  27145.98 2.714598e+04  9519.053      0  3.765088
Residuals      99108 282631.49 2.851753e+00        NA     NA 39.200360

Call:
lm(formula = dnase_max ~ psize, data = d)

Residuals:
    Min      1Q  Median      3Q     Max 
-29.120  -1.042  -0.334   0.565  76.783 

Coefficients:
              Estimate Std. Error t value Pr(>|t|)    
(Intercept) -2.8929053  0.0222170  -130.2   <2e-16 ***
psize        0.0248247  0.0001059   234.4   <2e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 2.163 on 99110 degrees of freedom
Multiple R-squared:  0.3567,    Adjusted R-squared:  0.3567 
F-statistic: 5.495e+04 on 1 and 99110 DF,  p-value: < 2.2e-16

             Df Sum Sq      Mean Sq  F value Pr(>F)   PctExp
psize         1 257148 2.571480e+05 54945.07      0 35.66586
Residuals 99110 463844 4.680093e+00       NA     NA 64.33414


```{r}
```
